
---
title: "Analysis of Q1 Relative to the Other Quadrants of the 20x20 Matrix"
author: "Ronald J. Botelho"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
    toc: true
    toc_depth: 2
header-includes:
  - \usepackage{setspace}
  - \doublespacing
---
```{r}
knitr::opts_chunk$set(
  echo = FALSE,      # Suppress code output
  warning = FALSE,   # Suppress warnings
  message = FALSE,   # Suppress messages
  error = FALSE,     # Suppress error messages
  fig.align = "center",  # Center-align figures
  fig.width = 7,     # Default figure width
  fig.height = 5     # Default figure height
)
```
```{r libraries, include=FALSE}
library(tidyverse)
library(ggplot2)
library(knitr)
library(markovchain)
library(entropy)
library(cowplot)  # For combining plots
# Add other libraries as needed
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.
```{r}

---

### 2. **Load and Preprocess the Data**

Add a chunk for data loading:
Load the datasets provided (`BlackBoxCuda1-A.csv`, `BlackBoxCuda1-B.csv`, `BlackBoxCuda1-C.csv`, `BlackBoxCuda_ver2.csv`) into data frames or matrices and prepare them for analysis.
```{r load-data, echo=TRUE}
file_a <- "path_to/BlackBoxCuda1-A.csv"
file_b <- "path_to/BlackBoxCuda1-B.csv"
file_c <- "path_to/BlackBoxCuda1-C.csv"
file_ver2 <- "path_to/BlackBoxCuda_ver2.csv"

data_a <- read.csv(file_a)
data_b <- read.csv(file_b)
data_c <- read.csv(file_c)
data_ver2 <- read.csv(file_ver2)

# Display summaries to confirm loading
summary(data_a)
summary(data_b)
summary(data_c)
summary(data_ver2)
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

